---
title: "Assignment 1 Markdown"
author: "Eva Burguete-Innocente 20154735"
date: "2023-01-10"
output:
  html_document: default
  pdf_document: default
---

[Link to my github](https://github.com/evainnocente/BIOL432_Assignment1) 

Load packages:
```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
```


1. Running Script 1 (dataGenerato.R)

```{r}
source('dataGenerato.R')
```

This script creates data frame with four columns: organism, limb width, limb length, and observer. These data were created by making vectors that randomly sampled 100 values from either a short list of species/observer names, or a normal distribution (for limb width/length)

2. Running Script 2 (volumeEstimato.R)

```{r}
source('volumeEstimato.R')
```

This script added a fifth column (limb volume) to the dataset created above. Limb volume was crudely estimated with the formula for volume of a cylinder, pir^2h, where limb width divided by 2 was the radius and limb length was the height.

3. Load the revised measurements.csv

```{r}
measurementsdata<-read.csv('measurements.csv')
```

4. Sort the data by species, observer, and limb volume

```{r}

measurementsdata%>%
  group_by(organism)

measurementsdata%>%
  group_by(observer)

measurementsdata%>%
  group_by(Volume)
```

5. Table showing average volume of each species

```{r}
measurementsdata%>%
        group_by(organism)%>%
        summarise(Avg_vol=mean(Volume))
```

6. Table showing number of observations for each combination of species and observer

```{r}
measurementsdata%>%
        group_by(organism,observer)%>%
        summarise(N=n())
```

7. A single box plot showing key features of the distributions of volumes for each species

```{r}

boxplot<-ggplot(aes(x=organism,y=Volume,fill=organism),data=measurementsdata)+geom_boxplot()+scale_fill_manual(values = c("blue", "green", "orange", "red","yellow"),name="Species")+labs(title = "Distributions of Limb Volume for Each Species",
       y = "Limb volume", x = "Species")
boxplot
```

8. Multi-panel plot of frequency histograms for each species.

```{r}

histogram<-ggplot(aes(x=Volume,fill=organism),data=measurementsdata)+geom_histogram(bins=35)+labs(title = "Frequency of Limb Volume for Each Species",
       y = "Frequency", x = "Limb volume")+facet_wrap(vars(organism))+
  scale_fill_manual(values = c("blue", "green", "orange", "red","yellow"),name = "Species")
histogram


```

