---
title: "Regex"
author: "Eva Burguete-Innocente"
date: "`r Sys.Date()`"
output: html_document
---

Link to my assignment 5 repository:
https://github.com/evainnocente/Assignment-5

Importing my measurements.csv file from my Week 1 assignment.

```{r}
MData<-read.csv("C:/Users/evain/OneDrive - Queen's University/university/BIOL 432/Week 1/measurements.csv")

```

Using dplyr and regular expressions to replace the genus name in the Organism column with the first letter of the word and a period (.). I named this column Sp. 

```{r}
library(dplyr)

MData<-MData%>%
  mutate(Sp=sub("(\\w)\\w+","\\1.", MData$organism))

#Checking whether it worked

head(MData)
```

I replaced the organism column with the Sp column I made above and reordered them so that Sp was the first column.

```{r}
MData<-MData%>%
  select(Limb_width,Limb_length,observer,Volume,Sp)%>%
  relocate(Sp)

#Checking if it worked

head(MData)

```

I saved this data set as a new csv file called MeasShort.csv. 

```{r}
write.csv(MData,"C:/Users/evain/OneDrive - Queen's University/university/BIOL 432/Week 1\\MeasShort.csv",row.names=FALSE)
```

